---
title: "Examples"
author: "Hervé Biancotto"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library('plotivol')
```

This is a collection of examples generated with plotivol package. This section illustrates how to use the function plotImpiedVol.

## Basic
The basic use of plotImpliedVol only requires a data frame.

```{r, fig.width=7, fig.height=5}
plotImpliedVol(df)
```

## Only ouput implied volatilities
No plots are created.

```{r}
plotImpliedVol(df, plotting=FALSE)
```

## Choose option type
The user can display results for only calls or only puts.

```{r, fig.width=7, fig.height=5}
plotImpliedVol(df, type='call')
```


## Choose a display style
The user can see volatility curves by strike, moneyness or delta.

```{r, fig.width=7, fig.height=5}
plotImpliedVol(df, style='delta')
```


## Combining type and style choices
In this example, the user requires only puts by delta

```{r, fig.width=7, fig.height=5}
plotImpliedVol(df, type='call', style='delta')
```
